Methods for Large Scale Learning to Rank

### 2014-09-10 report/Chapters/Results.tex
metingen-todo
results

>>>>

Figure \ref{fig:speedup_train_time} shows that speed-up is sub-linear such that the training time converges to a constant unit of time somewhere within the range of 150-200 seconds. This time is likely to be caused by Hadoop job scheduling overhead, this presumption is strengthened by long waiting periods between the separate MapReduce jobs that form a training iteration.
